\documentclass[conference]{IEEEtran}
\usepackage{times}

\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}

\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Anonymous)
   /Title  (AutoDex Rebuttal)
   /CreationDate (D:20260325120000)
   /Subject (Robotics)
   /Keywords (Dexterous;Grasping)
}

\definecolor{R1}{RGB}{0,128,0}
\definecolor{R2}{RGB}{0,0,200}
\definecolor{R3}{RGB}{200,0,0}
\definecolor{AC}{RGB}{128,0,128}

\newcommand{\rone}{{\color{R1}R1}}
\newcommand{\rtwo}{{\color{R2}R2}}
\newcommand{\rthree}{{\color{R3}R3}}
\newcommand{\acmark}{{\color{AC}AC}}

\renewcommand{\thetable}{R-\arabic{table}}
\renewcommand{\thefigure}{R-\arabic{figure}}


\newcommand{\rssparagraph}[1]{{\bf #1.}}

\begin{document}

\title{AutoDex [Paper-ID: 99]\vspace{-1cm}}
\maketitle
\thispagestyle{empty}

We thank the reviewers for recognizing the importance of bridging the sim-to-real gap ({\color{R1}R1}, {\color{R3}R3}), the ``clear quantitative argument for real-world filtering'' and ``coverage-preserving selection design'' ({\color{R2}R2}), and the inclusion of both successful and failed grasps ({\color{R3}R3}). We address key concerns below.

\rssparagraph{[\rone, \rthree, \acmark] The necessity of real-world validation}
We compared DR filtering (friction $\times$[range], mass $\times$[range]) against real execution on [N] grasps. [FP]\% of DR-passing grasps failed on the real robot (false positives, due to unmodeled dynamics such as finger-pad deformation and cable backlash). Conversely, [FN]\% of DR-rejected grasps actually succeeded on the real robot (false negatives, valid grasps unnecessarily discarded by DR).

[\rthree, \acmark] Despite this, we still use simulation as a coarse filter (high friction, low gravity) to remove clearly invalid grasps (no contact, penetration) while preserving borderline candidates for real validation.

\rssparagraph{[\rtwo, \rthree, \acmark] Strengthened evidence for physical validity}
We expanded our evaluation and report category-level statistics where each group has $n \geq 100$ trials.

\vspace{-0.2cm}
\begin{table}[h]
\centering
\scriptsize
\begin{tabular}{ll|cccc}
\toprule
& & Wood & Plastic & Metal & Paper \\
\midrule
Material & Sim-val.   & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
         & Real-filt. & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
\midrule
& & Table & Wall & Drawer & Clutter \\
\midrule
Scene    & Sim-val.   & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
         & Real-filt. & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
\midrule
\multicolumn{2}{l|}{Aggregate} & \multicolumn{2}{c}{Sim: {[X]}$\pm${[X]}} & \multicolumn{2}{c}{Real: {[X]}$\pm${[X]}} \\
\bottomrule
\end{tabular}
\vspace{6pt}

{\small \textbf{Table R-1.} Validation by category ($\pm$95\% CI)}
\label{tab:category_validation}
\end{table}
\vspace{-0.3cm}
\noindent Real-filtered grasps consistently outperform sim-validated across all categories.

\rssparagraph{[\rthree, \acmark] Scalability of the multi-camera setup}
The pipeline is hardware-agnostic (camera, arm, hand are modular). Calibration: $\sim$40 board images ($\sim$10 min) + automated hand-eye ($\sim$10 min). The 24-cam setup is a research choice; our pipeline works with 2 RGB cameras, though pose estimation degrades (Table III: 4-cam ADD-S 1.17mm vs 0.31mm, success 51\% vs 62\%). Dense multi-view helps under hand occlusion (avg [X]\%), but camera count is a per-lab trade-off.

\rssparagraph{[\rtwo, \acmark] Efficiency compared to teleoperation}
AutoDex: [X] grasps/hr, [X] min human time/grasp (object placement only). Teleop: [X] grasps/hr, continuous operator presence (body suit, 22-DoF control), limited to [X] hrs/session (fatigue, Xsens charging), with significant throughput variation between novice and expert operators. AutoDex produces consistent results regardless of operator skill, runs unattended overnight, and scales linearly with additional robots. Infrastructure costs (robot, cameras) are shared; teleop adds Xsens MVN Awinda (\$[X]) + per-session setup overhead.

\rssparagraph{[\rtwo, \rthree] Grasp selection and scenario coverage}
[\rthree] Our procedural constraints span the combinatorial space of planar boundaries: Wall (1-side), Shelf (2--3 sides + ceiling), and Box (4-sides). This covers all feasible grasping scenarios; the only excluded case (fully enclosed) is inherently infeasible.

[\rtwo] Sim solvability saturates at $\sim$[X]\% ($N$=1000: [X]\%, $N$=5000: [X]\%). This ceiling exists because our test scenes are generated without guaranteeing a feasible solution; some obstacle configurations completely enclose the object, leaving no valid approach direction. Despite this saturation, at our practical validation budget ($N$=100), constraint-aware greedy selection achieves [X]\% vs [X]\% for random

\vspace{-0.2cm}
\begin{table}[h]
\centering
\scriptsize
\begin{tabular}{l|cccc}
\toprule
& Baseline & Base. (real-filt) & Ours & Ours (real-filt) \\
\midrule
$N$=10 & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
$N$=30 & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} & {[X]}$\pm${[X]} \\
\bottomrule
\end{tabular}
\vspace{6pt}

{\small \textbf{Table R-2.} Physical scenario solvability (\%$\pm$95\% CI)}
\end{table}
\vspace{-0.3cm}
\noindent[\rtwo, \acmark] Table R-2 is a physical version of Table I. It confirms that geometric solvability (IK, collision) transfers reliably from sim to real, as robot kinematics and obstacle geometry are known precisely. The gap between Ours and Ours (real-filt) reveals where contact dynamics cause failures that simulation cannot predict. This is the asymmetry our pipeline exploits: simulation for geometry, real execution for contact. 
\rssparagraph{[\acmark, \rone, \rthree] Scope and contributions}
[\acmark, \rthree] We clarify AutoDex's contribution beyond engineering. While the real-world validation pipeline itself is an engineering effort, it enables something previously unavailable: physically-grounded grasp data free from human demonstration bias. Teleoperation datasets are inherently biased toward operator-preferred approach paths; AutoDex decouples grasp generation from execution, allowing any generation method (BODex, RL policies, human priors) to be validated on real hardware. This generator-agnostic design is a methodological contribution, not a single-use BODex extension.
Beyond automation, we address the core scalability bottleneck of real validation: the coverage-preserving selection algorithm maximizes the information gained per costly real execution, ensuring diverse constraint coverage within a limited budget. This is not simply ``running more grasps''; it formalizes \emph{which} grasps to validate as a combinatorial optimization problem.

[\rone, \acmark] The current dataset focuses on stable grasps, an intentional scope decision. Stable grasping under environmental constraints remains an open problem: no physically-validated dataset existed even for this foundational task. The pipeline naturally extends to functional grasps by replacing the generation method with one targeting task-specific objectives (e.g., tool-use orientation), while the validation and selection stages remain unchanged.

[\rthree] AutoDex is complementary to sim/DR, not a replacement. Large-scale sim data captures broad distributional priors; our physically-validated data provides high-fidelity labels for fine-tuning, following the established paradigm of pretraining on large-scale data and fine-tuning on task-specific real data. This makes AutoDex empirically meaningful even at 1.6K trajectories.

\rssparagraph{[\rtwo] Dataset statistics}
51 objects in Table IV have 100 trials each (1,678 trajectories). The remaining 49 objects have 3 trials each as a held-out test set. We will complete 100 trials for all 100 objects before camera-ready, scaling the dataset to $\sim$10K trajectories. Failure breakdown will be included in the revision.

{
  \small
  \bibliographystyle{plainnat}
  \bibliography{references}
}

\end{document}
